### 2019-10-01 conflog.tex

\subsubsection{I Hotel}

Dinner on Friday night will be hosted at the I Hotel. The I Hotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds. Catering is provided by University Catering which avoids a 20\% gratuity charge because of its association with the University of Illinois. This expansion is set to be completed by Fall 2020. We will be hosting a social at the 77 Club in Memorial Stadium, which is just a brief walk up the street. Information about the I Hotel expansion is included in Appendix D. Cost of transportation to and from the I Hotel and 77 Club are discussed in the budget section.

@@

$\textbf{The Garden Hotel Urbana}$\\
When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities. The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees. It features complimentary breakfast for its guests every morning. This will also be the location of the opening ceremony dinner. Since this hotel is just beyond walking distance from the main conference activities (2.2 miles), we will hire four Peoria Charter busses to shuttle attendees to and from the Union every 10 minutes. Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 7am to 5am the following day for weekdays, and every 30 minutes on weekends.\\ 
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_king.jpg}
		\subcaption{King Suite}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_queen.jpg}
		\subcaption{Queen Double}
	\end{subfigure}
	\caption{Garden Urbana Hotel rooms}		
\end{figure}

@@

$\textbf{Marriott TownePlace Suites}$\\
In the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TownePlace Suites. Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave, dishes, and dining area. Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired. The hotel offers internet access for a maximum of 3 devices per room. The hotel is located on Green Street and the Illini Union a mere five-minute walk away. For $\$7$ a day, guests may park in a parking garage with 8ft clearance.\\
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room1.jpeg}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room2.jpeg}
	\end{subfigure}
	\caption{Marriott Rooms: Left, a queen double. Right, a king single}		
\end{figure}

@@

\textbf{Thursday Night}\\
Communicating the science of nuclear energy remains one of the chief challenges of our field. The opening dinner of this conference will focus on science communication and the people behind the science. Science communication requires more than the recitation of raw data to be effective. By telling our own, diverse backstories, we become more effective science communicators. Speakers will be asked to speak to their own backstory as a nuclear advocate and how their story makes them a more effective communicator.\\\\
\indent\textbf{Friday Night}\\
The second dinner will be themed around networking and professional-development and how these critical tools have value beyond finding jobs. Communities like ANS thrive on the exchange of ideas and knowledge. The student conference plays an essential role by connecting the burgeoning minds of the next generation with the wisdom of established professionals. This dinner will consist of tables organized by company/national lab, or by topic/discipline area, to allow students and professionals to mingle, promoting the exchange of ideas.\\\\ 
\indent\textbf{Saturday Night}\\
The closing dinner of the conference will be a call to action for student attendees. Ours is a generation faced with challenges on a scale never witnessed by humanity, and we will only successfully address these challenges through the engagement of as many bright young minds as possible. The speakers for this night will be asked to address ways we all can take individual responsibility for the grand challenges of our age by using our own unique skills to tackle problems like climate change and energy poverty from every angle imaginable.\\ 
\subsection{Travel and Transportation}

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Table \ref{table:airfare} shows the round-trip, non-stop, airfare costs for the first weekend of April. Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip. While travel from airport to hotel can be managed by train (Amtrak/Metra), the conference planning committee excluded this option due to the added complexities of getting from the airport to train station, and train station to hotel with the associated costs of doing so. We recommend Peoria Charter because it is the most direct option for travel from O'Hare Aiport to the Illini Union. Due to the central location of UIUC, driving might be a good option for some schools and individuals. Table \ref{table:ground} shows the approximate driving times and costs from several universities.

>>>>

\subsubsection{I Hotel}
Dinner on Friday night will be hosted at the I Hotel. The I Hotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds. Catering is provided by University Catering which avoids a 20\% gratuity charge because of its association with the University of Illinois. This expansion is set to be completed by Fall 2020. We will be hosting a social at the 77 Club in Memorial Stadium, which is just a brief walk up the street. Information about the I Hotel expansion is included in Appendix D. Cost of transportation to and from the I Hotel and 77 Club are discussed in the budget section.

@@

$\textbf{The Garden Hotel Urbana}$\\
When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities. The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees. It features complimentary breakfast for its guests every morning. This will also be the location of the opening ceremony dinner. Since this hotel is just beyond walking distance from the main conference activities (2.2 miles), we will hire four Peoria Charter buses to shuttle attendees to and from the Union every 10 minutes. Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 7am to 5am the following day for weekdays, and every 30 minutes on weekends.\\ 
>>>>>>> upstream/master
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_king.jpg}
		\subcaption{King Suite}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_queen.jpg}
		\subcaption{Queen Double}
	\end{subfigure}
	\caption{Garden Urbana Hotel rooms}		
\end{figure}

@@

$\textbf{Marriott TowneSuites}$\\
The Marriott TowneSuites is the professional's designated hotel; and, in the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TowneSuites. Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave,dishes, and dining area. Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired. The hotel offers internet access for a maximum of 3 devices per room. The hotel is located on Green Street and the Illini Union a mere five-minute walk away. For $\$7$ a day, guests may park in a parking garage with 8ft clearance.\\

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room1.jpeg}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room2.jpeg}
	\end{subfigure}
	\caption{Marriott Rooms: Left, a queen double. Right, a king single}		
\end{figure}

@@

\textbf{Thursday Night}\\
Communicating the science of nuclear energy remains one of the chief challenges of our field. The opening dinner of this conference will focus on science communication and the people behind the science. Science communication requires more than the recitation of raw data to be effective. By telling our own, diverse backstories, we become more effective science communicators. Speakers will be asked to speak to their own backstory as a nuclear advocate and how their story makes them a more effective communicator.\\\\
\indent\textbf{Friday Night}\\
The second dinner will be themed around networking and professional-development and how these critical tools have value beyond finding jobs. Communities like ANS thrive on the exchange of ideas and knowledge. The student conference serves plays an essential role by connecting the burgeoning minds of the next generation with the wisdom of established professionals. This dinner will consist of tables organized by company/national laboratory or by topic/discipline area to allow students and professionals to mingle, promoting the exchange of ideas.\\\\ 
\indent\textbf{Saturday Night}\\
The closing dinner of the conference will be a call to action for student attendees. Ours is a generation faced with challenges on a scale never witnessed by humanity, and we will only successfully address these challenges through the engagement of as many bright young minds as possible. The speakers for this night will be asked to address ways we all can take individual responsibility for the grand challenges of our age by using our own unique skills to tackle problems like climate change and energy poverty from every angle imaginable.\\ 
\subsection{Travel and Transportation}

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Table \ref{table:airfare} shows the round-trip, non-stop, airfare costs for the first weekend of April. Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip. While travel from airport to hotel can be managed by train (Amtrak/Metra), the conference planning committee excluded this option due to the added complexities of getting from the airport to train station, and train station to hotel with the associated costs of doing so. We believe the charter bus to be the best route of action as it picks up travelers directly at the arrivals gate and brings them to the Illini Union. Due to the central location of UIUC, driving might be a good option for some schools and individuals. Table \ref{table:ground} shows the approximate driving times and costs from several universities.

### 2019-10-01 socials.tex

\subsubsection{Illini Union Rec Room Lockout}
The Illini Union Rec Room is located in the basement of the Union building. A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at the Illini Union! This space can accompany up to 150 people, with extra tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.
\vspace{0.5cm}\newline
% Illini Union Rec Room Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
	\end{subfigure}	
	\caption{Illini Union Rec Room}	
\end{figure}

\subsubsection{77 Club at Memorial Stadium}
Memorial Stadium is not only home to the Fighting Illini football team, but also to exquisite event space overlooking Zuppke Field. The sixth level of Memorial Stadium is home of the magnificent 77 Club, which honors Illini great, the ``Galloping Ghost'' Red Grange. This 5,020 square foot space is located midfield and features an outdoor patio area overlooking the city of Champaign, for a combined total space of 9,740 square feet. This event will take place following dinner at I Hotel Conference Center, and is just a short and scenic walk away past the State Farm Center (formerly the historic Assembly Hall). Tables will be set up around a stage featuring live music and a dance floor and drinks will be served. This is the perfect event to incorporate a little bit of Illinois history with music, dancing, and socializing! 
\vspace{0.5cm}\newline
% 77 Club Picture
\begin{figure}[H]

@@

%% Reserve for Pour Bros. social %%%
\subsubsection{Pour Bros. Taproom in Downtown Champaign}
Welcome to Illinois' first pour-your-own taprooms. Pour Bros. Taproom is located in the heart of the historic downtown Champaign area and features 28 pour-your-own taps: beers, ciders, meads and wine\ldots all poured by you, one ounce at a time. Socialize over the vintage games Pour Bros has to offer: skeeball, bubble hockey, steel tip darts, DAGZ and more! If you are feeling more on the leisurely side, Pour Bros features live music in a spacious and comfortable seating area for you to get your networking on.
\vspace{0.5cm}\newline
% Pour Bros Picture
\begin{figure}[H]

	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.4\linewidth]{pour_bros2.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{pour_bros1.png}
	\end{subfigure}	
	\caption{Pour Brothers Taproom}	
\end{figure}

\subsubsection{Barn Dance: A Proud Midwestern Tradition}
Barn dances are a staple event at UIUC. Socialize in a unique environment with games of corn-hole and other midwestern fun. Various barns are used for dancing and mingling by many of the student organizations on UIUC campus, such as Farm Lake barn which hosts dozens of barn dances annually. Other barns may be best suited for the student conference social events, such as Hudson Farm, which offers a corporate event or professional social events option which can accommodate up to 300 guests with an alcohol service available and friendly, helpful service. Like socials in the past student conferences, the barn may be used and a third party service can be hired to bring the square dance, swing dance, two step and cowboy boogie to the barn dance floor! 
\vspace{0.5cm}\newline
% Barn Dance Hudson Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.4\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{barn_dance1.png}
	\end{subfigure}%
	\begin{subfigure}{0.4\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{barn_dance2.png}
	\end{subfigure}	
	\caption{Hudson Farm Barn.}	
\end{figure} 
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.4\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{farmlake1.jpg}
	\end{subfigure}%
	\begin{subfigure}{0.4\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{farmlake2.jpg}
	\end{subfigure}	
	\caption{Farm Lake Barn}	
\end{figure}

\subsubsection{Under 21 Social: University of Illinois Ice Arena}
For students under the drinking age that cannot attend the Pour Bros. Taproom social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union. It was built in 1931 and offers a unique option for skating get-togethers from broomball and hockey to group skating parties. The Ice Arena is a 55,000 square foot facility and is the only one in Champaign-Urbana. The dimensions of the rink are 192' by 115' with a 1,200 seat arena surrounding. There are four public locker rooms, four party areas, and two Zambonis in the facility. The Center Ice Cafe offers hot chocolate, coffee, smoothies, fountain drinks, and more to quench your thirst.  Snacks and concession items are also available.
\vspace{0.5cm}\newline
% Ice Arena Picture
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{ice_arena.png}
	\caption{The UIUC Ice Arena}
\end{figure}

>>>>

\subsubsection{Barn Dance: A Proud Midwestern Tradition}
Barn dances are a staple event at UIUC. Socialize in a unique environment with games of corn-hole and other midwestern fun. Various barns are used for dancing and mingling by many of the student organizations on UIUC campus, such as Farm Lake barn which hosts dozens of barn dances annually. Conference attendees will be encouraged to dress up in country-style attire or costume for this Thursday evening event. Like socials in the past student conferences, the barn may be used and a third party service can be hired to bring the square dance, swing dance, two step and cowboy boogie to the barn dance floor! 
\vspace{0.5cm}\newline
% Barn Dance Hudson Picture
%\begin{figure}[H]
%	\centering
%	\begin{subfigure}{0.4\textwidth}
%		\centering
%		\includegraphics[width=0.9\linewidth]{barn_dance1.png}
%	\end{subfigure}%
%	\begin{subfigure}{0.4\textwidth}
%		\centering
%		\includegraphics[width=0.9\linewidth]{barn_dance2.png}
%	\end{subfigure}	
%	\caption{Hudson Farm Barn.}	
%\end{figure} 
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.4\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{farmlake1.jpg}
	\end{subfigure}%
	\begin{subfigure}{0.4\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{farmlake2.jpg}
	\end{subfigure}	
	\caption{Farm Lake Barn}	
\end{figure}

\subsubsection{77 Club at Memorial Stadium}
Memorial Stadium is not only home to the Fighting Illini football team, but also to exquisite event space overlooking Zuppke Field. The sixth level of Memorial Stadium is home of the magnificent 77 Club, which honors Illini great, the ``Galloping Ghost'' Red Grange. This 5,020 square foot space is located midfield and features an outdoor patio area overlooking the city of Champaign, for a combined total space of 9,740 square feet. This event will take place following dinner at I Hotel Conference Center, and is just a short and scenic walk away past the State Farm Center (formerly the historic Assembly Hall). Tables will be set up around a stage featuring live music and a dance floor and drinks will be served, along with hosting raffles with nuclear and Illinois trivia. This is the perfect event to incorporate a little bit of Illinois history with music, dancing, and socializing! 
\vspace{0.5cm}\newline
% 77 Club Picture
\begin{figure}[H]

@@

\subsubsection{Illini Union Rec Room Lockout}
The Illini Union Rec Room is located in the basement of the Union building. A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at The Garden Hotel. This space can accompany up to 150 people, with extra overflow space with tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities. This will be an alcohol free social option for Thursday night, and a bar social will be reserved as well for this night.
\vspace{0.5cm}\newline
% Illini Union Rec Room Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
	\end{subfigure}	
	\caption{Illini Union Rec Room}	
\end{figure}

\subsubsection{Bars in the Downtown Champaign District} 
The downtown Champaign area on the north-east block of University Ave. and Neil St. offers a selection of casual, approachable, and fun bars for 21+ guests of Illinois who wish to spend the night out rather than attend the Illini Union Rec Room. Reservations will be made in advance and several bars can accompany up to 100 patrons or more in the area. Some of the recommended bars that the conference planning committee recommend that would be great sponsorship opportunities are Pour Bros. Taproom (up to 100 guest reservation), Guido's Bar and Grill (private lower level space that seats up to 100 with a capacity of 230), and Barrelhouse 34 (has a cozy rooftop lounge if weather permits). Conveniently, the recommended bars are just a couple of blocks from each other, and transportation will be available to get people to and from the downtown Champaign area to the Illini Union.
\vspace{0.5cm}\newline
% Pour Bros Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
	\end{subfigure}	
	\caption{Pour Brothers Taproom}	
\end{figure}

% Guido's and Barrelhouse Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{guidos.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{barrelhouse.png}
	\end{subfigure}	
	\caption{Guido's (left) and Barrelhouse (right)}	
\end{figure}

%\subsubsection{Pour Bros. Taproom in Downtown Champaign}
%Welcome to Illinois' first pour-your-own taprooms. Pour Bros. Taproom is located in the heart of the historic downtown Champaign area and features 28 pour-your-own taps: beers, ciders, meads and wine\ldots all poured by you, one ounce at a time. Socialize over the vintage games Pour Bros has to offer: skeeball, bubble hockey, steel tip darts, DAGZ and more! If you are feeling more on the leisurely side, Pour Bros features live music in a spacious and comfortable seating area for you to get your networking on.

%\subsubsection{Under 21 Social: University of Illinois Ice Arena}
%For students under the drinking age that cannot attend the Pour Bros. Taproom social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union. It was built in 1931 and offers a unique option for skating get-togethers from broomball and hockey to group skating parties. The Ice Arena is a 55,000 square foot facility and is the only one in Champaign-Urbana. The dimensions of the rink are 192' by 115' with a 1,200 seat arena surrounding. There are four public locker rooms, four party areas, and two Zambonis in the facility. The Center Ice Cafe offers hot chocolate, coffee, smoothies, fountain drinks, and more to quench your thirst.  Snacks and concession items are also available.
%\vspace{0.5cm}\newline
%% Ice Arena Picture
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.8\textwidth]{ice_arena.png}
%	\caption{The UIUC Ice Arena}
%\end{figure}
